Formalization of Abstract Rewriting

### 2025-02-14 Relations/Paper/Main.tex
Added todo file.
added authorrunning
ARS paper plan

@@

\begin{abstract}
    We present a constructive formalization of Abstract Reduction Systems (ARS)
     in the Agda proof assistant, focusing on the results given in Term Rewriting 
     Systems (Terese). We define a taxonomy of concepts related to termination and 
     confluence and investigate their relationships between each other and their 
     classical counterparts. We identify, and eliminate where possible, the use of classical 
     logic in the proofs of standard ARS results. Our analysis leads to refinements and mild
      generalizations of classical termination and confluence criteria.
\end{abstract}
\input{Introduction.tex}
\input{Definitions.tex}
\input{Implications.tex}
\input{Counterexamples.tex}
\input{Well-foundedness.tex}

@@

>>>>

\authorrunning{A. Polonsky and S. Arkle}

@@

\begin{abstract}
    We present a constructive formalization of Abstract Reduction Systems (ARS)
     in the Agda proof assistant, focusing on the results given in Term Rewriting
     Systems (Terese). We define a taxonomy of concepts related to termination and
     confluence and investigate their relationships between each other and their
     classical counterparts. We identify, and eliminate where possible, the use of classical
     logic in the proofs of standard ARS results. Our analysis leads to refinements and mild
      generalizations of classical termination and confluence criteria.
\end{abstract}
\input{Introduction.tex}
\input{Definitions.tex}
\input{Implications.tex}
\input{Counterexamples.tex}
\input{Well-foundedness.tex}
\input{FinalTODO.tex}

@@

Plan of the paper:

1. Introduction: 2 pages.
2. Definitions/setup: 2 pages. [WIP]
3. Formalization of Chapter 1 Terese, including Newman's Lemma: 2 pages [Still needs to be done]
- Statements (not proofs!) of key propositions and theorems in Agda code
4. Implications, hierachies, figures, and counterexamples: 4-5 [draft in report]
5. Classical principles and well-foundedness: 3 pages
6. Miscellaneous facts: 1 page
7. Related and future work: 1 page
